The Hajada Imputation Test

### 2020-06-28 2-2-the-hajada-imputation-test.Rmd
Może nawet ostateczne poprawki

There are many different ways of dealing with missing values. Depending on their quantity and properties, various methods turn out to be the best. The fact is, there is no one universal best method of imputation, and different problems require various solutions. Using one and the same solution for each dataset is certainly not the best option, but sometimes it is convenient or even necessary to focus on one particular method without much insight into its effect - for example, when time limits us or when, due to the complexity of the algorithm or class of problems, we are forced to choose only one method. In this chapter we will take a look at several popular imputation methods and try to compare them with each other, including ranking of algorithms taken into account and finally choosing the best one. For this purpose, we will analyse imputation times and predictions scores for several machine learning classification algorithms on various datasets.

>>>>

There are many different ways of dealing with missing values. Depending on their quantity and properties, various methods turn out to be the best Using one and the same solution for each dataset is certainly not the best option, but sometimes it is convenient or even necessary to focus on one particular method without much insight into its effect - for example, when time limits us or when, due to the complexity of the algorithm or class of problems, we are forced to choose only one method. In this chapter we will take a look at several popular imputation methods and try to compare them with each other, including ranking of algorithms taken into account and finally choosing the best one. For this purpose, we will analyse imputation times and predictions scores for several machine learning classification algorithms on various datasets.
